Modeling the Linux page cache for accurate simulation of data-intensive applications

### 2021-07-27 paper_io_sim.tex
Fixed figure placement

        \subsection{Single-threaded execution (Exp 1)}

        % \todo[inline]{Henri: In the paragraph below I would remove the ``The first read was ... data." sentence.}

@@

            \begin{figure*}
                \begin{subfigure}{\linewidth}
                    \centering
                    \includegraphics[width=\linewidth]{result/multi/figures/multi_local.pdf}
                \end{subfigure}
                \caption{Concurrent results with 3~GB files, 5 repetitions (\textit{Exp 2})}
                \label{fig:multi_local}
            \end{figure*}
            \begin{figure*}
                \begin{subfigure}{\linewidth}
                    \centering
                    \includegraphics[width=\linewidth]{result/multi/figures/multi_nfs.pdf}
                \end{subfigure}
                \caption{NFS results with 3~GB files, 5 repetitions (\textit{Exp 3})}
                \label{fig:multi_nfs}
                \end{figure*}
        \subsection{Concurrent applications (Exp 2)}

@@

        \begin{figure}[b]
                \centering
                \includegraphics[width=0.95\linewidth]{result/nighres/figures/nighres_errors.pdf}
            \caption{Real application results (\textit{Exp 4})}
            \label{fig:nighres}
            \end{figure}

@@

        \begin{figure}
            \centering
            \includegraphics[width=0.95\linewidth]{result/multi/figures/simulation_time.pdf}
            \caption{Simulation time comparison. \wrench-cache scaled
            linearly with the number of concurrent applications, albeit
            with a higher overhead than \wrench.}
            \label{fig:multi_time}
            \end{figure}

@@

    Page cache simulation can be instrumental in a number of studies. For
    instance, it is now common for HPC clusters to run applications in
    Linux control groups (cgroups), where resource consumption is limited,
    including memory and therefore page cache usage. Using our simulator,
    it would be possible to study the interaction between memory allocation
    and I/O performance, for instance to improve scheduling algorithms or
    avoid page cache starvation~\cite{zhuang2017}. Our simulator could also
    be leveraged to evaluate solutions that reduce the impact of network
    file transfers on distributed applications, such as burst
    buffers~\cite{ferreiradasilva-fgcs-bb-2019}, hierarchical file
    systems~\cite{islam2015triple}, active storage~\cite{5496981}, or
    specific hardware architectures~\cite{hayot2020performance}. We expect
    page cache simulation to drastically reduce the simulation error in all
    these scenarios, with substantial consequences on study conclusions.

    Relevant extensions to this work include more
    accurate descriptions of anonymous memory usage in applications, 
    which strongly affects I/O times through writeback caching. File access patterns
    might also be worth including in the simulation models,
    as they directly affect page cache content.

>>>>

        \begin{figure*}[h!]
            \centering
            \begin{subfigure}{0.95\linewidth}
                \centering
                \includegraphics[width=\linewidth]{result/multi/figures/multi_local.pdf}
            \end{subfigure}
            \caption{Concurrent results with 3~GB files, 5 repetitions (\textit{Exp 2})}
            \label{fig:multi_local}
        \end{figure*}
        \subsection{Single-threaded execution (Exp 1)}
        \begin{figure*}[h!]
            \centering
            \begin{subfigure}{0.95\linewidth}
                \centering
                \includegraphics[width=\linewidth]{result/multi/figures/multi_nfs.pdf}
            \end{subfigure}
            \caption{NFS results with 3~GB files, 5 repetitions (\textit{Exp 3})}
            \label{fig:multi_nfs}
            \end{figure*}
        % \todo[inline]{Henri: In the paragraph below I would remove the ``The first read was ... data." sentence.}

@@

        \subsection{Concurrent applications (Exp 2)}

@@

        \begin{figure}[h!]
                \centering
                \includegraphics[width=0.95\linewidth]{result/nighres/figures/nighres_errors.pdf}
            \caption{Real application results (\textit{Exp 4})}
            \label{fig:nighres}
            \end{figure}

@@

@@

    Page cache simulation can be instrumental in a number of studies. For
    instance, it is now common for HPC clusters to run applications in
    Linux control groups (cgroups), where resource consumption is limited,
    including memory and therefore page cache usage. Using our simulator,
    it would be possible to study the interaction between memory allocation
    and I/O performance, for instance to improve scheduling algorithms or
    avoid page cache starvation~\cite{zhuang2017}. Our simulator could also
    be leveraged to evaluate solutions that reduce the impact of network
    file transfers on distributed applications, such as burst
    buffers~\cite{ferreiradasilva-fgcs-bb-2019}, hierarchical file
    systems~\cite{islam2015triple}, active storage~\cite{5496981}, or
    specific hardware architectures~\cite{hayot2020performance}. We expect
    page cache simulation to drastically reduce the simulation error in all
    these scenarios, with substantial consequences on study conclusions.
    \begin{figure}[t]
        \centering
        \includegraphics[width=0.95\linewidth]{result/multi/figures/simulation_time.pdf}
        \caption{Simulation time comparison. \wrench-cache scaled
        linearly with the number of concurrent applications, albeit
        with a higher overhead than \wrench.}
        \label{fig:multi_time}
        \end{figure}
    Relevant extensions to this work include more
    accurate descriptions of anonymous memory usage in applications, 
    which strongly affects I/O times through writeback caching. File access patterns
    might also be worth including in the simulation models,
    as they directly affect page cache content.
